### 2018-10-04 manuscript.tex
rebutal++

In order to compute CWT, we interfaced the \texttt{WaveletComp} package\cite{schmidbauer_waveletcomp_2018} in \texttt{rethomics}. 
This interface allowed us to average the result of the five consecutive days in the time/period domain over one circadian day both for the two representative animals (Fig~\ref{fig:fig-6}D)
and for the population(Fig~\ref{fig:fig-6}E).

>>>>

We implemented specific utilities to compute and display CWT spectrograms in \texttt{rethomics}, based on the \texttt{WaveletComp} package\cite{schmidbauer_waveletcomp_2018}. 
We then used this interface to average the result of the five consecutive days in the time/period domain over one circadian day both for the two representative animals (Fig~\ref{fig:fig-6}D)
and for the population(Fig~\ref{fig:fig-6}E).
